The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-05 paper/ms.tex
Try new travis LaTeX

This finding has many implications for the study of the dynamics of stars in
what is normally considered the regime of the epicyclic approximation:
quasi-harmonic oscillations around a circular ``guiding center orbit.'' Here
we consider those implications for the prospect of distribution function
fitting.

>>>>

This finding has many implications for the study of the dynamics of stars in
what is normally considered the regime of the epicyclic approximation:
quasi-harmonic oscillations around a circular ``guiding center orbit.''
